Search-based Synthesis of Network Intrusion Detection Rules

### 2019-09-07 paper/paper.tex
adding related presentations

\Mar{--------------------------------- parei aqui}

@@

This section 1) presents an example of a network attack, 2) shows an
example rule of Suricata to detect this attack and alert system
administrators about it, and 3) illustrates how \tname{} performs to
synthesize the corresponding rule.

>>>>

\Fix{summarize how the technique works}

\Fix{summarize results}

@@

This section 1) presents an example of a network attack, 2) shows an
example rule of Suricata to detect this attack and alert sys admins
about it, and 3) illustrates how \tname{} performs to synthesize the
corresponding rule.
